\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[a4paper,margin=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
{\LARGE \textbf{Artem Sidnev}}\\[0.35em]
Middle Backend / DevOps Engineer\\[0.35em]
\href{mailto:a.sidnevart@gmail.com}{a.sidnevart@gmail.com} \quad
\href{https://t.me/sidnevart}{t.me/sidnevart} \quad
\href{https://github.com/sidnevart}{github.com/sidnevart}
\end{center}

\vspace{0.6em}

\section*{Summary}
Middle Backend / DevOps engineer at T-Bank. I build high-load systems, data platforms, and practical AI/LLM automation. Strongest where reliability, critical-flow speed, and measurable business impact matter.

\section*{Work Experience}
\textbf{T-Bank} \hfill 2025 -- present\\
\textit{Middle Backend / DevOps Engineer}
\begin{itemize}
  \item Build and scale a cashback offer targeting platform for managers (audiences over 1.5 years of history and ~30M transactions/day).
  \item Accelerated a critical production audience-building flow by ~5x after migration and optimizations.
  \item Reduced diagnosis time for common issues by 20--40 minutes with early validation and clearer errors.
  \item Automated manager routines: minus 10--15 minutes per run and up to 40--60 manual hours per month.
  \item Implemented AI code review in GitLab and an AI CI job for automated refactoring and MR prep.
  \item Built n8n automations and a RAG onboarding agent: AI workflows ~1.5x faster, token usage down up to 3x.
\end{itemize}

\section*{Key Projects}
\begin{itemize}
  \item Cashback Offer Targeting Platform (big-tech internal product).
  \item AI Automation for Internal Workflows (GitLab AI review, AI CI, n8n, RAG onboarding).
  \item Commercial Real Estate Analytics (auctions + market comparables + Telegram delivery).
  \item Personalized Mobile Banking Chat (Rust, transaction-based personalization).
\end{itemize}

\section*{Stack}
Languages: Java, Kotlin, Go, Rust, TypeScript\\
Data \& Messaging: PostgreSQL, ClickHouse, Redis, Kafka\\
Focus: high-load systems, data pipelines, AI automation, integrations

\end{document}
